Detecting Facial Expressions in Professional Tennis Matches

### 2017-08-08 Report06-12.Rmd
Auto stash before merge of "master" and "steffMVP/master"

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE)

@@

```{r Player, fig.cap = c("This stacked bar chart allows consideration ", "of the interaction between two image attributes. \\label{fig:DDPbgshot}")}

@@

ggplot(data=ALLmetaIMGPlayers) +
     geom_bar(aes(x=bg, fill = shotangle), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) +
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Angle the face was captured from")

>>>>

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.)

@@

```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}

@@
